Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-31 main-disk-model.tex
temp

\newcommand{\bw}{bw}
\newcommand{\br}{br}

@@

If the entire memory required by  task ~$u\in V$ fits in the available memory of processor~$p_j$,
    then the execution time of this task on this processor is expressed as $\frac{w_u}{s_j}$.
However, if the memory requirement of the task exceeds the available memory on the processor, 
then task can still be executed there, but it will be slowed down. Indeed, 
%    albeit slower.
the part of memory requirement that exceeds the available memory on processor~$j$, $availM_j$, 
will be offloaded to the disk, slowing down the execution:

    \[
        w_{real} = \frac{w_u}{s_j} +  q_s \times   (m_u - availM_j) , %   \frac{q_s \times w_u}{s_j} \frac{m_i - M_j}{m_i}
    \]
where $q_s$ is the slowdown coefficient, and $(m_u - availM_j)$ is the part 
of the task memory that needs to be offloaded.
\AB{Svetlana please check, I think we said in the end that we use absolute value 
of the amount of memory not fitting locally...}
%    \skug{check this equation}
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

The goal is to find a schedule of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized. 
\AB{no more memory constraint, now the lack of memory just slows down the execution, correct?
I'll probably add a few sentences here...}
% while respecting memory constraints. \skug{do we still formulate it like that?}
    %If a processor runs out of memory to execute
%a task mapped on it, the schedule is said to be {\em invalid}.

Since tasks are subject to variability, we aim at minimizing the actual makespan
achieved at the end of the execution, while decisions may be taken building
on the estimated task parameters.
\AB{Probably need to clarify offline vs online problem at some point...}

Note that the problem is already NP-hard even in the homogeneous case and 
without memory constraints, because of the DAG structure of the application. 
Hence, we focus on the design of efficient scheduling heuristics. 
%\hmey{Mention NP-hardness due to being more general than NP-hard problem?}

>>>>

\newcommand{\bw}{bw}
\newcommand{\br}{br}
\newcommand{\Moff}[1]{m^{\text{off}}_{#1}}

@@

If the entire memory required by  task ~$u\in V$ fits in the available memory of processor~$p_j$,
    then the execution time of this task on this processor is expressed as $\frac{w_u}{s_j}$.
However, if the memory requirement of the task exceeds the available memory on the processor, 
then task can still be executed there, but it will be slowed down. Indeed, 
%    albeit slower.
the part of memory requirement that exceeds the available memory on processor~$j$ for task~$u$, 
denoted by $\Moff{u}$, %M\text{off}_u$, 
will be offloaded to the disk, slowing down the execution:

    \[
        w_{real} = \frac{w_u}{s_j} +  q_j \times  \Moff{u}, %  (m_u - Mav_u) , %   \frac{q_s \times w_u}{s_j} \frac{m_i - M_j}{m_i}
    \]
where $q_j$ is the slowdown coefficient for $p_j$. %, and $(m_u - Mav_u)$ is the part 
%of the task memory that needs to be offloaded.
\AB{Svetlana please check, I think we said in the end that we use absolute value 
of the amount of memory not fitting locally...}
%    \skug{check this equation}
%We assume that all processors are connected with the same bandwidth~$\beta$.
%    \hmey{Maybe mention that variable bandwidths are part of future work...?}

@@

In the {\bf offline setting}, the goal is to find a {\em schedule} of the DAG~$G$ for the $k$ processors,
so that the makespan (total execution time) is minimized. Formally, a schedule contains:
\begin{itemize}
\item for each task, its processor allocation and starting time, 
as well as the amount of data offloaded for the execution of the task; 
\item for each read and write operation to disk, the starting time of the operation; 
\item for each data and processor, the time intervals during which the file is available
on the local memory of the processor (once it has been generated or read, and before 
it is used or evicted). 
\end{itemize}

\AB{I'm confused again about the offloading model, we need to talk}

%\AB{no more memory constraint, now the lack of memory just slows down the execution, correct?
%I'll probably add a few sentences here...}
% while respecting memory constraints. \skug{do we still formulate it like that?}
    %If a processor runs out of memory to execute
%a task mapped on it, the schedule is said to be {\em invalid}.

\medskip
We also consider the {\bf online setting} where tasks are subject to variability, 
and then we know the exact time required to complete a task only when 
it ends its execution. Hence, we aim at minimizing the actual makespan
achieved at the end of the execution, while scheduling decisions 
have to be taken building
on the estimated task parameters.
In this case, we do not build the whole schedule offline, but we build
it on the fly, as tasks become ready (their predecessor tasks have been completed). 
%\AB{Probably need to clarify offline vs online problem at some point...}

Note that the offline problem is already NP-hard even in the homogeneous case and 
without memory constraints (i.e., no need to offload data onto disk), and even for
a graph without precedence constraints (independent tasks). 
%because of the DAG structure of the application. 
Hence, we focus on the design of efficient scheduling heuristics. 
%\hmey{Mention NP-hardness due to being more general than NP-hard problem?}
